Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-08 ms.tex
Modify Section 3
From 5b62b56:
============

In ms.tex,

(*) Modify Section 3

% In wide-field measurements, the steep rise in subtended solid angle near the horizon for a fixed delay bin size significantly enhances the integrated emission near the horizon delay limits. This is found to be true for diffuse emission even on wide antenna spacings because their foreshortening towards the horizon makes them sensitive to large angular scales that match the inverse of their foreshortened lengths. Typically, an antenna is most sensitive towards its primary field of view relative to the rest of the sky, which in conjunction with the aforementioned wide-field effects results in a characteristic {\it pitchfork} signature in the delay spectrum.

% Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal. And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint. Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation. In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.

@@

The MWA instrument configuration, EoR observations, and data analysis used in this study are already described in \citet{thy15} and references therein. In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings. Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith. The database contains 14 snapshots satisfying these criteria. Two of these snapshots were found to contain amplitude and phase artifacts for a significant duration across different baselines. Hence, they have been excluded from our analysis.

>>>>

@@

The MWA instrument configuration, EoR observing strategy, and analysis procedure applied to individual snapshots used in this study are already described in \citet{thy15} and references therein. In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings. Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith. The database contains 14 snapshots satisfying these criteria. Two of these snapshots were found to contain amplitude and phase artifacts for a significant duration across different baselines. Hence, they have been excluded from our analysis.
